\subsection{Remarks}
When using the ADD process to create an architecture for the ReMeS system, 
the dept of the iterations was limited to two levels in most cases. 
In some cases, however, another decomposition (level 3) was needed to explain some 
concepts a bit better. 

The concept of iterations was used to describe different phases of the ADD project.
An iteration is seen as a complete decomposition to the lowest level starting from the
highest level. An iteration ends when there are no more decompositions to be done on a lower level
while still dealing with the original top level components.
Each time the component called Other functionality gets decomposed to address some previously unresolved
quality attributes and/or use cases, a new iteration begins.

It is however the case in this assignment that a limited amount of quality attributes have been supplied
to use as main drivers for the add process. Due to this, some functional requirements can not be linked
or deduced from the supplied quality attributes. When this is the case, those functional requirements will not 
be used to instantiate components in the architecture by using the ADD process alone, since ADD stands for 
Attribute Driven Design. 
Most of these use cases are related to the user interface. There are no given quality attributes addressing 
any of the user interface functionalities. These functionalities will be added (albeit in a lower level of detail) in the last iteration
and in the final architecture described in section \ref{sec:FinalArch}. It is however not a strict ADD-methodology that is used for those remaining functions.

In some of the lowest level decompositions, the decomposition seems to be driven solely by functional requirements without quality attributes. 
Sometimes it is possible that the non functional drivers for an iteration are already met but another decomposition for child components is needed to illustrate some remaining functional requirements. This is situation is however different from what is discussed in the previous paragraph where there were no non-functional drivers to begin with.

