\subsubsection{PF1: Remote monitoring module sends new data}
The remote monitoring modules will send data about the amount of consumed utilities, the battery state, 
signal level, leak detection, etc. ReMeS needs to respond correctly to this information.
\begin{itemize}
	\item \textbf{Source:} internal
	\item \textbf{Stimulus:} 
		A remote monitoring module sends a new trame of data containing valuable information.
	\item \textbf{Artifact:} System services
	\item \textbf{Environment:} Normal mode
	\item \textbf{Response:} 
		\begin{itemize}
			\item The trame contains data about the amount of consumed utilities. ReMeS will update its database
					so that the database has more correct values.
			\item The trame contains a byte indicating that the battery is running low. ReMeS will notify a ReMeS
					operator and will also notify the client about the battery status.
			\item The trame contains a byte indicating that the signal of the remote module connection is low. ReMeS
					will notify the client and a ReMeS operator about this alarm.
			\item The trame's data indicates that there is a leak detected by the monitoring module. ReMeS will
					control the remote valve if available. ReMeS will notify the client about the leak and in the case
					of a gas leak, ReMeS will also notify the emergency services for gas.
		\end{itemize}
	\item \textbf{Response measure:} 
		\begin{itemize}
			\item If the trame indicates that there is a leak, this alarm will receive the highest priority. ReMeS will notify the user within 5 minutes. If the
					leak is a gasleak, ReMeS will notify the emergency services within maximum 2 minutes. The remote
					valve (if installed) will also be controlled within maximum 2 minutes.
			\item The other trames are receiving a lower priority. They will be handled within maximum 30 minutes.
		\end{itemize}
\end{itemize}