\subsubsection{PF2: A user requests data through the web portal}
The web portal allows users to view their own consumption data. It also allows users to view
personalized tips on how to lower their utility consumption. We assume that the web portal is available (see availability of the web portal)
\begin{itemize}
	\item \textbf{Source:} external
	\item \textbf{Stimulus:} 
		\begin{itemize}
			\item The user logs in into the web portal
			\item The user requests his/her measurement data over the last weeks, months or years
			\item The user edits his/her contact information
			\item The user edits the configuration of the remote monitoring module
			\item The user requests consumption advice
		\end{itemize}
	\item \textbf{Artifact:} System services
	\item \textbf{Environment:} Normal mode
	\item \textbf{Response:}
		\begin{itemize}
			\item If the user logs in into the web portal, ReMeS will check if the username and password are consistent.
					If they are, ReMeS will provide a token for this user and the user will have access to his/her services.
			\item If the user edits his/her contact information, ReMeS will update its database accordingly.
			\item In the case that the user edits the configuration of the remote monitoring module, ReMeS will update this information
					in its database. ReMeS will also send a configuration trame to the remote monitoring module.
			\item When the user requests measurement data or consumption advice, ReMeS will obtain the data from its database, process
					this data and show it to the user.
		\end{itemize}
	\item \textbf{Response measure:}
		\begin{itemize}
			\item Logging in into the web portal is a fairly easy task for ReMeS. From the moment the request is sent until
					the user sees the logged in information shouldn't take more than 30 seconds. In peak times, where the servers
					are overloaded, this could take longer.
			\item Updating contact information also is an easy task. This operation shouldn't, as logging in, take more than 30 seconds.
			\item Requesting and processing consumer data for one user is a slightly harder task. Therefor this could take almost 60 seconds
					until the user receives the processed data.
			\item If the user wishes to edit the configuration of the remote monitoring module, ReMeS will send a configuration trame to the 
					module. From the moment the user indicated the changes until the moment where the remote monitoring module changes its
					configuration could take up to 5 minutes. This because of the possible delay on the external communication channel.
		\end{itemize}
\end{itemize}