\subsubsection{Av3: Consumption prediction model updates}
The consumption prediction model that ReMeS creates for the utility companies is send
periodically to these companies. Updates on the model can also be requested by the companies.
ReMeS will send these updates within reasonable time.
\begin{itemize}
	\item \textbf{Source:} internal and external
	\item \textbf{Stimulus:}
		\begin{itemize}
			\item ReMeS will send these models periodically to the companies. It is time to send a new update.
			\item A newer, better version of the model is available. ReMeS will send this model as fast as it can
			\item A utility company requests a certain model. ReMeS will send this model as fast as possible
		\end{itemize}
	\item \textbf{Artifact:} ReMeS Utility Production Planning
	\item \textbf{Environment:} normal execution
	\item \textbf{Response:} 
		In each case ReMeS will send the latest available model. If ReMeS Utility Production Planning has almost
			finished calculating a newer version of the model, we will wait until this newer version is calculated
			and send this newer version to the utility companies.
	\item \textbf{Response measure:} 
		\begin{itemize}
			\item In the case that it is time to send a periodical update of the model, ReMeS will wait for the newest model
				only if the calculation will be finished within 30 minutes. The average time between two periodical updates
				should be around 24 hours.
			\item If a newer, better version of the model is available, ReMeS will try to send this model as fast as possible. The
					delivery time depends solely upon the delay of the communication channel ReMeS uses to communicate with the
					utility company.
			\item If a utility company requests	a certain model (yearly, monthly, weekly, ...) ReMeS Utility Production Planning first
					has to compose this model. This should take 30 minutes at max. If the utility company requests the newest available
					daily model, ReMeS will send the latest model it has calculated unless the calculation of a newer model
					will be finished within 30 minutes.
		\end{itemize}
\end{itemize}