\subsubsection{Bad Signal Alarm}

\paragraph{Use Case Name}
Bad Signal Alarm
\paragraph{Primary actor}
Remote monitoring module: The module that works with a remote connection.
\paragraph{Interested Parties}
ReMeS technician: Sometimes a ReMeS technician must go on site to solve the problem with a remote module. \\
ReMeS operator: If a remote monitoring module hasn't been repaired within a certain period of time, a ReMeS operator must call and help the client to repair the problem. \\
Client: A client will be notified and will try to fix the problem with the bad signal of the remote module.
\paragraph{Preconditions}
The client has a remote monitoring module installed
\paragraph{Normal Flow}
\begin{enumerate}
	\item ReMeS detects that a remote monitoring module hasn't sent any data for a certain period of time.
	\item ReMeS creates an alarm.
	\item ReMeS notifies the client and the ReMeS call center about this alarm.
	\item The client solves the problem with the module.
\end{enumerate}

\paragraph{Alternative Flow}
\begin{enumerate}
	\item[4a.] The client is unable to solve the problem.
	\begin{enumerate}
		\item[4a1.] A ReMeS operator contacts the client.
		\item[4a2.] The ReMeS operator tries to look for the problem and its resolution.
	\end{enumerate}
	\item[4b.] The client and the ReMeS operator are unable to solve the problem.
	\begin{enumerate}
		\item[4b1.] A ReMeS technician is dispatched to the user.
		\item[4b2.] The ReMeS technician solves the problem with the remote monitoring module.
	\end{enumerate}
\end{enumerate}


\paragraph{Postcondition}
The bad signal problems with the remote module are now solved.
