\subsubsection{Create user profile for business user.}

\paragraph{Use Case Name}
Create user Profile for \textbf{business} user.
\paragraph{Primary actor}
Potential client: An employee of a company wanting to become a client of ReMeS. \\
ReMeS call center employee: Whenever a potential client calls to request a new profile, the ReMeS operator needs to send an empty contract to the potential client.
\paragraph{Interested Parties}
Utility Company: The utility company of which a client wishes to become a client of ReMeS.
\paragraph{Preconditions}
The company in question can not already be a client of ReMeS.
\paragraph{Normal Flow}
\begin{enumerate}
	\item An \textbf{employee of a company} calls the ReMeS call center and requests the contract for becoming a \textbf{business} client to be sent to his
	address.
	\item A contract is sent to the provided address.
	\item The \textbf{employee} fills in the contract and sends it back to ReMeS.
	\item The \textbf{company} is added to the ReMeS system as a \textbf{business} user.
	\item A confirmation letter is sent to the \textbf{company}'s address by regular mail. 
	\item The \textbf{company} receives a letter containing an authentication token consisting of a user name and password. 
\end{enumerate}

\paragraph{Alternative Flow}
\begin{enumerate}

	\item[4a.] \textbf{The employee} filled in the wrong information and the contract is not valid. 
	\begin{enumerate}
		\item[4a1.] \textbf{The employee} is sent a letter explaining that there was a problem processing his request.
			\textbf{The employee} is also sent a new contract to be filled in.
		\item[4a2.] Goto step 3. 
	\end{enumerate}
	
\end{enumerate}

\paragraph{Postcondition}
The \textbf{company} is now a client of ReMeS and can login with his personal user name and password.
