\subsubsection{Profile Association}

\paragraph{Use Case Name}
Profile Association with remote monitoring module
\paragraph{Primary Actor}
ReMeS Operator: An operator at ReMeS who links the device to the user profile.\\
Client representative: A residential user or a representative for a business user.
\paragraph{Interested Parties}
Utility company: The Utility company's UIS wants to be informed of the outcome of this use case.\\
Regular Mail Service: The regular postal service which will transport and deliver the modules.
\paragraph{Preconditions}
The representative who will be provided a remote monitoring module has to be a residential,
 or a business client of ReMeS.
\paragraph{Normal Flow}
\begin{enumerate}
	\item The use case starts when a ReMeS operator gets the order to link a profile to a module.
	\item The ReMeS operator verifies that the monitoring module has an identification number that has not been used yet in the system. 
	\item The ReMeS operator creates a new entry in the system for the remote monitoring module.
	\item The ReMeS operator links the newly created entry to the user profile provided. 
	\item The ReMeS operator sends the module by regular mail to the address provided by the user profile
	\item The client representative receives the module. 
	\item Include use case \textit{Install module at location}.
	%\item The module is installed at the client location by a ReMeS technician.
	%\item The module signals the ReMeS central system that it is up and running at the installed location.
	\item The ReMeS operator receives confirmation from the system that installation has been successful.
	\item The ReMeS operator signals the UIS of the utility company in question that the customer in 
question now uses ReMeS.
\end{enumerate}

\paragraph{Alternative Flow}
\begin{enumerate}
	\item[5a.] In the user profile it is indicated that the user would rather pick up the module
at a ReMeS collection point. 
	\begin{enumerate}
		\item[5a1.] The ReMeS operator sends the module by regular mail to the ReMeS collection point indicated in the user Profile. 
		\item[5a2.] The client representative goes and picks up the module from the collection point.
	\end{enumerate}
\end{enumerate}

\paragraph{Postcondition}
The module is installed at the site and is linked to the user profile the module was intended for.
