\subsubsection{PF3: A new consumer has been added to ReMeS}
Whenever the utility companies that are a client of ReMeS gain new customers, these customers
also needs to be added to our ReMeS system. In order to do this, ReMeS needs to gain access to
the client's information to create a profile. Then ReMeS will create a username and password for
this client. Finally the client will be able to log in to the ReMeS web portal with his authentication token.
\begin{itemize}
	\item \textbf{Source:} external
	\item \textbf{Stimulus:} 
		A client of a utility company calls the ReMeS call center with the request to become a client of ReMeS.
	\item \textbf{Artifact:} System services
	\item \textbf{Environment:} Normal mode
	\item \textbf{Response:} 
		\begin{itemize}
			\item When the client calls the ReMeS call center, ReMeS will send a contract to the client's home address.
					The client will fill in this contract and send it back to ReMeS.
			\item When ReMeS receives the filled in contract, a new profile will be created in the ReMeS database. ReMeS
					will also generate an authorization token, consisting of a username and a password. This authorization token
					will be sent to the client. From now on, the client can log in using this data.
		\end{itemize}
	\item \textbf{Response measure:} 
		\begin{itemize}
			\item The time between the moment that the client calls the ReMeS call center until ReMeS receives the filled in contract
					can be up to 5 working days plus the time that the client takes to send back the filled in contract.
			\item Once ReMeS has received the filled in contract, it should only take maximum 1 day to activate the profile. Ofcourse
					the client will only receive the letter containing the authorization token 2-3 days later, depending on how fast
					the mail delivery service works.
		\end{itemize}
\end{itemize}