\subsubsection{Create user profile}

\paragraph{Use Case Name}
Create user Profile
\paragraph{Primary Actor}
A potential client: Whenever someone wants to join ReMeS, the future client first needs to request an account.\\
ReMeS call center employee: Whenever a potential client calls to request a new profile, the ReMeS operator needs to send an empty contract to the potential client.
\paragraph{Interested Parties}
Utility Company: The utility company of which the potential new client of ReMeS is a client of.
\paragraph{Preconditions}
The person in question can not already be a client of ReMeS.
\paragraph{Normal Flow}
\begin{enumerate}
	\item A person calls the ReMeS call center and requests the contract for becoming a residential client to be sent to his
	home address.
	\item A contract is sent to the provided home address.
	\item The person fills in the contract and sends it back to ReMeS.
	\item The person is added to the ReMeS system as a residential user.
	\item A confirmation letter is sent to the new user's home address by regular mail. 
	\item The new client receives a letter containing an authentication token consisting of a user name and password. 
\end{enumerate}

\paragraph{Alternative Flow}
\begin{enumerate}

	\item[4a.] The person filled in the wrong information and the contract is not valid. 
	\begin{enumerate}
		\item[4a1.] The person is sent a letter explaining that there was a problem processing his request.
				The person is also sent a new contract to be filled in.
		\item[4a2.] Goto step 3. 
	\end{enumerate}
	
\end{enumerate}

\paragraph{Postcondition}
The person in question is now a client of ReMeS and can login with his personal user name and password.
