\subsubsection{Remote Control Module De-activation}

\paragraph{Use Case Name}
Remote Control Module De-activation
\paragraph{Primary actor}
ReMeS Technician: A technician who removes the remote control module \\
Client: A client who needs his/her remote control module removed.
\paragraph{Interested Parties}
None
\paragraph{Preconditions}
The client must have a remote control module installed. The appointment for the technician is verified and 
the client has been reminded of the appointment.
\paragraph{Normal Flow}
\begin{enumerate}
	\item A ReMeS technician arrives at the location where the module is installed.
	\item The technician removes the remote control module from the utility net interface.
	\item The technician notifies ReMeS that the remote control module has been removed.
	\item ReMeS updates his information that the remote control module is no longer active.
	\item The technician finalizes the paperwork and asks for a signature.
\end{enumerate}

\paragraph{Alternative Flow}
\begin{enumerate}
	\item[1a.] There is nobody at the location where the module is installed who can grant access to the technician.
	\begin{enumerate}
		\item[1a1.] The technician notifies ReMeS that a new appointment must be made.
		\item[1a2.] The technician starts a new assignment.
		\item[1a3.] ReMeS requests the client to make a new appointment.
		\item[1a4.] The client makes a new appointment.
		\item[1a5.] The client is charged a fee for missing the appointment.
		\item[1a6.] Goto step 1.
	\end{enumerate}
\end{enumerate}

\paragraph{Postcondition}
The remote control module is removed from the location.
