%\subsection{Level 1}
TODO deze subsectie verwijderen :p
\subsubsection{Invoice Manager}
In this section we will address other architectural drivers who aren't addressed
	in the primary decomposition of ReMeS. We will discuss them and see if we can
	implement them in the current system, without having too much changes.
\paragraph{Architectural drivers}

\begin{itemize}
	\item \textbf{AV3: Third Party Billing Service failure}
	\begin{itemize}
		\item UC15: Generate invoice
	\end{itemize}
	It is possible that the connection to the third party billing service fails.
	In that case we cannot send new invoices to that service. ReMeS must detect
		this and make sure no billing requests are lost when the Third Party
		Billing Service fails. ReMeS should keep trying to send the invoice 5 times
		before notifying a ReMeS operator.
\end{itemize}


\paragraph{Tactics}
\begin{itemize}
	\item Availability
	\begin{itemize}
		\item Fault Detection\\
		ReMeS must detect when an error occurs with sending an invoice to the Third
			Party Billing Service. Whenever ReMeS sends an invoice, the Third Party
			Billing Service should send an acknowledgement back to ReMeS.
	\end{itemize}
\end{itemize}


\paragraph{Architectural Patterns}
We didn't decompose anything here, because the decomposition was already
	done in another iteration.


\paragraph{Verification and refinement of drivers}
None of the architectural drivers have been addressed in this component.
They will be delegated to child components.
\textbf{3th Party Billing Service Communicator}
\begin{itemize}
	\item \textbf{UC15: } Generate invoice
\end{itemize}
