\subsubsection{IUserInteraction}
\label{sec:IUserInteraction}
\paragraph{Interface Identity}
This interface is provided by the Application controller component. The main
	use of this interface is interaction with users outside the ReMeS system.
\paragraph{Resources Provided}
This interface has a wide variety of methods. Some of them are listed below.
\begin{itemize}
	\item{boolean login(AuthToken authToken)}\\
	A method to login into the Application controller.
	\item{void createBill(AuthToken authToken, UserInfo userInfo)}\\
	A method to request a new bill creation.
	\item{void giveFeedback(AuthToken authToken, Feedback feedback)}\\
	A method the customer can use to give feedback to a detected anomy by ReMeS.
	\item{void setAlarmRec(AuthToken authToken, UtilityType type, Recipient[] recipients)}\\
	A method the customer can use to set the recipients for certain alarms.
	\item{ConsumptionPrediction reqPrediction(AuthToken authToken, PredictionType type)}\\
	A method to request a new consumption prediction.
	\item{void createUser(AuthToken authToken, UserInfo userInfo)}\\
	A method to create a new user in the system.
	\item{void freqReconfig(AuthToken authToken, FreqProfile newFreq)}\\
	A method to reconfigure the frequency that a remote measurement module sends trames with.
\end{itemize}
This list of methods is incomplete. The IUserInteraction interface contains all kinds of methods for
	a user to interact with the system.
\paragraph{Data Type Definitions}
\begin{itemize}
	\item AuthToken\\
	The specific piece of information that can authenticate a user.
	\item UserInfo\\
	Data type that contains information of a user.
	\item Feedback\\
	Data type that contains the feedback of a customer. This feedback can be positive or negative.
	\item UtilityType\\
	The type of utility (gas, water, power).
	\item Recipient\\
	Data type that contains information on who to contact and how to contact that person.
	\item ConsumptionPrediction\\
	A computed consumption prediction.
	\item PredictionType\\
	The type of the requested consumption prediction. This structure contains the utility
		and the timeframe.
	\item FreqProfile\\
	Data type that contains information on the frequency that a remote measurement module sends trames with.
\end{itemize}
\paragraph{Exception Definitions}
\begin{itemize}
	\item UnauthorizedException\\
	This exception can be thrown by all methods of this interface (except for the login method). This exception
		is thrown when the requested method cannot be executed by the user.
\end{itemize}