\subsubsection{IDataBase}
\paragraph{Interface Identity}
This interface is provided by the Data storage component. Internally,
 each separate database instance in the Data storage component also provides
 this interface.
\paragraph{Resources provided}
\begin{itemize}
	\item{void create(CreateQuery q)}\\
	This is one of the four basic database access methods provided.
	This method signifies the creation of a record based on a given 
	query q.
	\item{void update(UpdateQuery q)}\\
	This is one of the four basic database access methods provided.
	This method signifies updating a record based on a given 
	query q.
	
	\item{DataTransferObject get(GetQuery q)}\\
	This is one of the four basic database access methods provided.
	This method signifies retrieving a record based on a given 
	query q. The information contained in this record will be returned
	as a DataTransferObject.
	\item{void remove(RemoveQuery q)}\\
	This is one of the four basic database access methods provided.
	This method signifies removing a record based on a given 
	query q.
	
\end{itemize}
\paragraph{Data Type Definitions}
\begin{itemize}
	\item CreateQuery\\
	This data type represents a database query of the creation category.
	This CreateQuery type is a subtype of the general Query data type. 
	\item UpdateQuery\\
	This data type represents a database query of the update category.
	This UpdateQuery type is a subtype of the general Query data type. 
	\item GetQuery\\
	This data type represents a database query of the retrieval category.
	This GetQuery type is a subtype of the general Query data type. 
	\item RemoveQuery\\
	This data type represents a database query of the remove category.
	This RemoveQuery type is a subtype of the general Query data type.
	\item DataTransferObject\\
	A data object that contains the information of a record in the Data storage.
\end{itemize}
\paragraph{Exception Definitions}
\begin{itemize}
	\item QueryFormatException\\
	This exception can be thrown when an argument representing a query to be executed, does not follow the expected formatting rules.
	\item DatabaseUnavailableException\\
	This exception can be thrown when the implementing component is unresponsive for any reason.
\end{itemize}
